mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-03-19 EMSOFT2016/diff/0221_thesis.tex
update

Although script languages are easy to use and read, their execution time are slower than C language's.
For embedded systems, the real-time properties such as estimation of worst-execution time are very important factors.
Therefore, it is difficult to apply the script languages to embedded systems.

@@

This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a strage device only once at the beginning and to transfer mruby application codes from a host to a target device.
The RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
%Specifically, a periodic handler of switching tasks is implemented.
%This paper evaluates the proposed framework in term of data transfer rate, overhead of periodic handler and execution time.

{\bf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
\item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
The loader supports the countinuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
In addition, synchronization of multiple tasks is also implemented.
\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

@@

\subsection{TECS}
\label{sec:TECS}
TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
TECS helps decrease difficulty because the generated component diagram can visualize the structure of whole software.
It can also help increase productivity and reduce development duplication because a common part of software is regarded as a component.

@@

As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
TOPPERS/HRP2 is an RTOS based on $\mu$ITRON \cite{par:microITRON} with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{par:ASP}, \cite{url:ASP}.

@@

\section{Design and Implementation}
\label{sec:Design and Implementation}
Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
The RiteVM reads the own bytecode and executes it.
The mruby applications run at the same time because of synchronization processing.
The RiteVM scheduler switches tasks as multiple tasks can run in concurrent.

@@

As an approach for multitask processing, the proposed framework provides the RiteVM scheduler which is a fair scheduler and runs multiple tasks equally.
The RiteVM scheduler is utilized only when application tasks have the same priority.
mruby applications can run in concurrent without developers calling the OS's function.
The application programs can also utilize the existing programs since the structures of the programs are not changed.

@@

A RiteVM scheduler is a periodic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
{\it rotateReadyQueue} is described as follows.

@@

Figure \ref{fig:cyclic_handler} shows a component diagram of the periodic handler.
The components of periodic handler consist of two components: CyclicHandler and CyclicMain.
CyclicHandler {\it cell} configures the periodic handler based on $\mu$ITRON.
Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
The periodic handler has five arguments: ID, attribute, periodic time, periodic phase and access pattern.
CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
CyclicMain {\it cell} is a component to perform the processing body of a periodic handler.
{\it rotateReadyQueue} is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
The attribute is used as an arguments of {\it rotateReadyQueue}.

Figure \ref{build_cyclic_handler} shows a build description that corresponds to the component diagram shown in Figure \ref{fig:cyclic_handler}.
In the part of CyclicHandler {\it cell}, configurations of a periodic handler is described such as attribute, cyclicTime and cyclicPhase.
In this case, the periodic handler is executed when it is generated because the attribute is {\it TA\_STA} that represents the periodic handler is in an operational state after the creation.
The periodic handler is executed every one msec.
In another part, the priority of CyclicMain {\it cell} is described.
RITEVM\_PRIORITY defines the priority of mruby tasks.
In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.

@@

In addition, the end of mruby applications is synchronized to accept the continuous loading.
The ending synchronization prevents a RiteVM whose application immediately finishes from waiting the next loading.
All of mruby applications finish at the same time, and all RiteVMs wait for receiving the next mruby application bytecodes.

@@

In the framework, RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove these components and also reuse them.
For example, if developers do not need the RiteVM scheduler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
This advantage of CBD saves developers the labor of rewriting a kernel configuration file.

In addition, the code size can decrease by developing with component-based. 
In the proposed framework, the advantage is applied in the Eventflag component.
The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
In addition, the components of Eventflag are built with {\it [optional]} in TECS.
{\it [optional]} means that the codes are run only when the call port is connected.
The .c file does not be rewritten even if developers do not use Eventflag.

\section{Experimental Evaluation}
\label{sec:Evaluation}
This section mentions experimental results and their consideration.
To analyze the advantages of the proposed framework, the evaluations are performed as follows.
\begin{itemize}
%    \item Execution time of the platform
    \item Size and time for transferred mruby bytecodes
    \item Execution time with singletasking, co-routine, and multitasking
    \item Overhead for periodic time
%    \item Synchronization of mruby applications
    \item Code size using the benefit of CBD 
\end{itemize}

@@

The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
The mruby application bytecode is smaller and faster than that of including mruby libraries in all terms.
The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
%In the proposed framework, developers send only mruby application and prepare mruby library in advance.
%Therefore, the design can send the bytecode faster.
In addition, the design can save the time to rewrite a storage/ROM device, and to restart an OS.
These advantages lead improvement of the software development efficiency.

@@

The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
In Figure \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is one msec.
%While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
This result shows the proposed design is superior to co-routine in terms of execution time.
Moreover, developers can utilize the scheduler practically because the overhead of the RiteVM scheduler is about 5 \%.
Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
%The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
%Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
The scheduler interrupts and switches tasks, which causes this overhead.

@@

Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
A lower limit of the periodic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
More than eight msec do not be evaluated in this paper because it is thought the larger periodic time influences applications.
%Each execution time of cyclic period is the same as the others.
%That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
The execution time decreases as the periodic time become larger, because the number of switching tasks decreases.
The execution time of one msec is only about 1 \% lager than that of eight msec.
The RiteVM scheduler with small periodic time can effectively execute multiple tasks because the periodic time overhead is not large.
%This results also shows the overhead becomes smaller as the periodic time is larger, because the overhead depends on the number of switching tasks.
%The smaller periodic time is better in multitasking due to concurrent and/or parallel processing.

@@

To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
(A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase as the number increases.
(B)'s .c file can be utilized without modification, regardless of the number of RiteVMs.
Moreover, lines of two .cdl files are equal.
The skillful component-based development brings this advantages such as the decrease of code lines and non-modified code, which leads high productivity and high maintainability.

\begin{table}[t]
    \centering
    \caption{Lines of .c and .cdl file for the number of RiteVM}
    \begin{tabular}{c||cc|c}
                & (A)       & (B)     & Diff  \\ \hline
        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
        .c (Modified)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
    \end{tabular}
    \label{tab:codesize}
\end{table}

@@

\begin{table*}[t]
    \centering
    \caption{Comparison of the proposed and previous work}
    \begin{tabular}{c||c|ccccccc}
        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Management} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparison}
\end{table*}
The open-source run-time systems for scripting languages have been proposed such as follow:
python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
The VM runs a significant subset of Python language with few resources on a micro-controller.
p14p can run multiple stackless green threads.

The Owl system is an embedded Python run-time system.
The Owl is a complete system for ARM Cortex-M3 micro-controllers.
The Owl toolchain produces relocatable memory images, that are directly runnable on the micro-controller, from Python code objects.
The interpreter of the Owl system is the same as that of python-on-a-chip.

@@

Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
The proposed framework supports the loader, the VM scheduler, and synchronization of application.

\section{Conclusion}
\label{sec:Conclusion}
This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheduler.
The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
The RiteVM scheduler makes multitasking more easily than the current mruby on TECS.
In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
The loader can improve the software development efficiency on mruby on TECS.
The RiteVM scheduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
%because of the low overhead.

The proposed framework is developed in component-base by TECS.
The facilities such as RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheduler can be easily removed.
Component-based development can increase productivity.

>>>>

Although script languages are easy to use and read, their execution time are slower than C language's.
For embedded systems, the real-time properties such as worst-execution time and response time are very important factors.
Therefore, it is difficult to apply the script languages to embedded systems.

@@

This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a strage device only once at the beginning and to transfer mruby application codes from a host to a target device.
The RiteVM scheuler enables developers to run multitasking programs more easily than mruby on TECS.
%Specifically, a cyclic handler of switching tasks is implemented.
%This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.

{\bf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
    \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
The loader supports the countinuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
In additon, synchronization of multiple tasks is also implemented.
\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

@@

\subsection{TECS}
\label{sec:TECS}
TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
TECS helps decrease complexity and difficulty because the generated component diagram can visualize the structure of whole software.
It can also help increase productivity and reduce development duplication  because a common part of software is regarded as a component.

@@

As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
TOPPERS/HRP2 is an RTOS based on $\mu$ITRON \cite{par:microITRON} with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{url:ASP}.

@@

\section{Design and Implementation}
\label{sec:Design and Implementation}
Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
The RiteVM reads the own bytecode and executes it.
The mruby applications run at the same time because of synchronization processing.
The RiteVM scheuler switches tasks as multiple tasks can run in concurrent.

@@

As an approach for multitask processing, the proposed framework provides the RiteVM scheuler which is a fair scheduler and runs multiple tasks equally.
The RiteVM scheuler is utilized only when application tasks have the same priority.
mruby applications can run in concurrent without developers calling the OS's function.
The application programs can also utilize the existing programs since the structures of the programs are not changed.

@@

A RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
{\it rotateReadyQueue} is described as follows.

@@

Figure \ref{fig:cyclic_handler} shows a component diagram of the cyclic handler.
The components of cyclic handler consist of two components: CyclicHandler and CyclicMain.
CyclicHandler {\it cell} configures the cyclic handler based on $\mu$ITRON.
Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
{\it rotateReadyQueue} is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
The attribute is used as an arguments of {\it rotateReadyQueue}.

Figure \ref{build_cyclic_handler} shows a build description that corresponds to the component diagram shown in Figure \ref{fig:cyclic_handler}.
In the part of CyclicHandler {\it cell}, configurations of a cyclic handler is described such as attribute, cyclicTime and cyclicPhase.
In this case, the cyclic handler is executed when it is generated because the attribute is {\it TA\_STA} that represents the cyclic handler is in an operational state after the creation.
The cyclic handler is executed every one msec.
In another part, the priority of CyclicMain {\it cell} is described.
RITEVM\_PRIORITY defines the priority of mruby tasks.
In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.

@@

In addtion, the end of mruby applications is synchronized to accept the continuous loading.
The ending synchronization prevents a RiteVM whose application immediately finishes from waiting the next loading.
All of mruby applications finish at the same time, and all RiteVMs wait for receiving the next mruby application bytecodes.

@@

In the framework, RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove these components and also reuse them.
For example, if developers do not need the RiteVM scheuler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
This advantage of CBD saves developers the labor of rewriting a kernel configuration file.

In additon, the code size can desrease by developing with component-based. 
In the proposed framework, the advantage is applied in the Eventflag component.
The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
In additon, the components of Eventflag are built with {\it [optional]} in TECS.
{\it [optional]} means that the codes are run only when the call port is connected.
The .c file does not be rewritten even if developers do not use Eventflag.

\section{Experimental Evaluation}
\label{sec:Evaluation}
This section mentions experimental results and their consideration.
To analyze the advantages of the proposed framework, the evaluations are performed as follows.
\begin{itemize}
%    \item Execution time of the platform
    \item Size and time for transferred mruby bytecodes
    \item Execution time with singletasking, co-routine, and multitasking
    \item Overhead for cyclic time
%    \item Synchronization of mruby applications
    \item Code size using the benefit of CBD 
\end{itemize}

@@

The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
The mruby application bytecode is smaler and faster than that of including mruby libraries in all terms.
The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
%In the proposed framework, developers send only mruby application and prepare mruby library in advance.
%Therefore, the design can send the bytecode faster.
In addition, the design can save the time to connect a storage/ROM device to restart an OS.
These advantages lead improvement of the software development efficiency.

@@

The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
This result shows the proposed design is superior to co-routine in terms of execution time.
The overhead of multitask is about 5 \% ($(multitask-singletask)/multitask$).
Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
%The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
%Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
The scheuler interrupts and switches tasks, which causes this overhead.

@@

Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
More than 10 msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
Each execution time of cyclic period is the same as the others.
That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.

@@

To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
(A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase in proportion to the number.
(B) is not modified, and can be utilized regardless of the number of RiteVMs.
Moreover, lines of two .cdl files are equal.
The skillfull component-based development brings this advantage such as the decrease of code lines, which leads high productivity and high maintainability.

\begin{table}[t]
    \centering
    \caption{Lines of .c and .cdl file for the number of RiteVM}
    \begin{tabular}{c||cc|c}
                & (A)       & (B)     & Diff  \\ \hline
        .c      & 134$+$8$\times$$\alpha $  & 130     & 4$+$8$\times$$\alpha$ \\
        .cdl    & 25$+$18$\times$$\alpha$   & 25$+$18$\times$$\alpha$ & 0     \\
        \multicolumn{3}{l}{  }\\
        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
    \end{tabular}
    \label{tab:codesize}
\end{table}

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|ccccccc}
        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparison}
\end{table*}
The open-source run-time systems for scripting languages have been proposed such as follow:
python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
The VM runs a significant subset of Python language with few resources on a microcontroller.
p14p can run multiple stackless green threads.

The Owl system is an embedded Python run-time system.
The Owl is a complete system for ARM Cortex-M3 microcontrollers.
The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
The interpreter of the Owl system is the same as that of python-on-a-chip.

@@

Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
The proposed framework supports the loader, the VM scheuler, and synchronization of application.

\section{Conclusion}
\label{sec:Conclusion}
This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
The loader can improve the software development efficiency on mruby on TECS.
The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
%because of the low overhead.

The proposed framework is developed in component-base by TECS.
The facilities such as RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheuler can be easily removed.
Component-based development can increase productivity and decrease complexity.
